Are populations like a circuit? The relationship between isolation by distance and isolation by resistance

### 2019-01-11 review-responses.tex

\begin{point}{\revref}
    $F_ST \neq$ Absolute divergence!!! . $F_ST$ is more a
    co-variance measure, and for instance heavily influence by sampling a batch
    of related individuals (whereas the mean of absolute divergence will be
    unchanged).
\end{point}

\reply{
}

\begin{point}{}
    You have your own implementation of resistance distance methods, by first
    extracting hitting times. However, you allow non-symmetric rates, something
    no existing resistance method would do. Given your observation that there
    is a lot degeneracy for resistance times (adding skew stuff to hitting
    times), this introduces uncertainty that likely cannot be broken such as
    with coalescence methods. This could drive the high uncertainty in Fig 5
    upper right. Given your good results for Fig. 4 for the symmetric case,
    this is a bit surprising. Maybe run one scheme where you FIX to a single
    symmetric movement rate between each pair of demes. This setting would be a
    fairer comparison (and be much closer to what EEMS etc. actually do -- they
    do not even try to infer asymmetric rates).
\end{point}

\reply{
    This is something we were considering doing. 
    We decided to allow symmetric migration in the resistance distance case 
    in order to make the two methods as similar as possible, 
    although it could arguably be more useful to compare them
    when they are implemented how they would be in practice.
}

@@

\begin{point}{\revref}
    Do you actually use this tensor product for the movement
    rates anywhere? And seems Eq. 7 (which has no Tensor product) is all you
    need.
\end{point}

\reply{
    We included this because we think it's a nice compact way to write, code, 
    and think about the equation,
    and the tensor product equation is actually the one used in the R code.
    It is correct that the equations are equivalent.
}

\begin{point}{Line 115:}
    Not all $ZC$ skew-symmetric would translate to valid Generators 
    $G + Z$. The diagonal elements of G have another condition (they have to be minus
    the sum of all other jumping rates). Would be interesting to explore this a
    bit more -- overall what the dimensionality this degeneracy is (implicit
    function theorem), and also if there are simple toy examples where they pop
    up.
\end{point}

\reply{
    Thank you for catching this.
    You are correct that in addition to $ZC$ being skew-symmetric,
    the rows of $Z$ must also sum to zero.
    The second part is also a good point, 
    but probably beyond the scope of this paper.
}

@@

\begin{point}{Paragraph beginning \revref:}
    Maybe move this section in front of the inference part, as it is useful to
    know the most ``fundamental'' limit of resistance distances.
\end{point}

\reply{
}

\begin{point}{Fig. 7:}
    With EEMS one can see very suspiciously the 4x4 sampling structure - there
    are red dots in almost all 3x3 centers of the sampling squares. Since EEMS
    is quite fast, could you increase the resolution of sampling?
\end{point}

\reply{
    More samples could be added for the EEMS runs, 
    but doing so would have the drawback 
    that the two methods would no longer be using the same data for inference. 
    We could add a note pointing out that the $3 \times 3$ grid of slow 
    moving spaces is an artifact.
}

@@

    I find the main deficiency to be the lack of any analysis of real data. All
    experiments are carried out on simulated data only. This is a puzzling omission.
    The authors went to the trouble of creating an R package (which is good), so
    clearly they intend for the method to be used in practice. Personally, I would
    hesitate to publish the results obtained from a method which had not previously
    been verified to produce reasonable answers in real data. This really feels like
    something the authors ought to have included. It is not necessary that the data
    be novel -- reanalyzing (say) the African elephant dataset in the EEMS paper
    would provide for an interesting comparison (even if it cannot be done at an
    equivalent spatial resolution) and would also go long way towards reassuring
    practitioners.
\end{quote}

\begin{point}{}
    ``Bayesian inference of movement rates'': In their model the authors assume
    that many entries of the migration rate matrix are zero, and place an
    exponential prior on the rest. Is it safe to assume that we will always
    want to constrain rates between discontiguous cells to zero? Also, given
    the valid concerns that they raise elsewhere about identifiability and
    power, I wonder if the authors considered placing a sparse prior on the
    entire G matrix, enabling the model to adapt to the amount of signal while
    shrinking other migration rates to zero. This might have the effect of
    making the resulting non-zero estimates more stable. (I realize that this
    raises potential problems for inference if the underlying graph becomes
    disconnected.)
\end{point}

\reply{
    Whether or not it is reasonable to assume there is no long distance migration
    depends on the population under study. 
    There are cases where it might be a good idea to allow it.
    Putting a sparse prior on all of $G$ is a good idea for future improvements, 
    although it would probably be appropriate for the prior probability of a value
    to be non-zero to be much higher for adjacent demes as compared to non-adjacent ones, 
    which would also likely prevent the graph from becoming disconnected very often.
    Since disconnecting the graph would result in some infinite coalescence times, 
    these steps would be rejected anyway.
}

@@

\begin{point}{}
    The discussion of ill-conditioning is welcome. From experience, it often
    feels like coalescent-based methods have little power to accurately
    estimate migration unless the rates are large. It might be interesting to
    shift emphasis from estimation to the slightly easier problem of testing:
    how good are these methods at distinguishing between a given null and an
    alternative hypothesis (say, barrier vs. no barrier) for the rate matrix G?
    I think the gain of using a coalescent model might be more apparent in this
    case.
\end{point}

\reply{
}

\begin{point}{}
    This method is computationally limited by equation (7), which has a
    complexity of $O(d^6)$ for the product Markov chain on d demes mentioned a
    few lines below. At least, that is the cost for solving (7) exactly -- but
    given the noisiness of the matrix C, there may be little point in doing
    that anyways. I wonder if the authors have thought at all about obtaining
    an approximate solution to (7), where the error in approximation is chosen
    to in some way to balance out the statistical error inherent in C / D. It
    may also be possible to leverage the fact that the solution G is sparse
    here.  (This is more of a suggestion for future research rather than a
    suggestion for revision.)
\end{point}

\reply{
    Solving (7) directly for $G$ and $\gamma$ with a noisy $C$ is extremely difficult
    even in cases small enough to just use least squares; 
    it typically resulted in some negative values unless there is very little noise in $C$.
    In order to solve for $C$ from $G$ and $\gamma$, 
    we briefly experimented with the Jacobi method. 
    While it seemed to converge fairly reliably, 
    at the grid sizes where it was computationally advantageous to use it over solving exactly, 
    it would still take a very long time for the MCMC to converge
    due to the large number of parameters.
    Devoloping a way to reduce the number of parameters in a way similar to EEMS
    while still allowing asymmetric migration is a good direction for future implementations.
}

@@

\begin{point}{\revref}
     Do the authors have any other guidance on how to discretize the landscape?
\end{point}

\reply{
    Aside from making decisions based on prior knowledge of the geography, 
    the sampling locations might lend themselves to being grouped together in a certain way.
}

@@

\begin{point}{}
    Does the issue of having negative entries of G (lines 112-117, Appendix A)
    arise during the course of MCMC sampling, and if so, how is it dealt with?
\end{point}

\reply{
    No. The proposal distribution includes taking the absolute value of parameters.
}

### 2019-02-16 isolation_by_coalescence.tex
ack cronk

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
to Brad Shaffer and Evan McCartney-Melstad for discussions about landscape modeling,
and to John Novembre, Hussein Al-Asadi and Benjamin Peter for help with EEMS
and general input.
We would also like to gratefully acknowledge the immense positive impact that Brad McRae \citep[1966--2017;][]{lawler2018tribute}
has had on landscape genetics and conservation biology through the introduction of landscape resistance.
We hope this paper helps to carry forward this work.
Work on this project was supported by funding from
the Sloan Foundation and the NSF (under DBI-1262645) to PR.

>>>>

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
to Brad Shaffer and Evan McCartney-Melstad for discussions about landscape modeling,
to John Novembre, Hussein Al-Asadi and Benjamin Peter for help with EEMS
and general input,
and to Quentin Cronk and Armando Geraldes for consultations about the \emph{Populus} results.
We would also like to gratefully acknowledge the immense positive impact that Brad McRae \citep[1966--2017;][]{lawler2018tribute}
has had on landscape genetics and conservation biology through the introduction of landscape resistance.
We hope this paper helps to carry forward this work.
Work on this project was supported by funding from
the Sloan Foundation and the NSF (under DBI-1262645) to PR.
